Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-04-16 manuscript/manuscript.Rmd
Move functions into package

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library(MASS)
library(readr)
library(dplyr)
library(ggplot2)
library(stringr)
library(magrittr)
library(tidyr)
library(reshape2)
library(scales)
library(grid)
library(geomorph)
library(rjson)
library(ipred)
library(vegan)
library(lubridate)
library(directlabels)
library(BAMMtools)
library(knitcitations)
library(kfigr)
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
source("functions.R")
```

>>>>

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library("MASS")
library("readr")
library("dplyr")
library("ggplot2")
library("stringr")
library("magrittr")
library("tidyr")
library("reshape2")
library("scales")
library("grid")
library("geomorph")
library("rjson")
library("ipred")
library("vegan")
library("lubridate")
library("directlabels")
library("BAMMtools")
library("knitcitations")
library("kfigr")
library("fish.reliability")
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
```
